%\documentclass{aa}
%\documentclass[referee]{aa} % for a referee version
\documentclass[preprint]{aa}
\pdfoutput=1

\bibliographystyle{aa}
%\AuthorCallLimit=200
\usepackage{booktabs}
\usepackage{csvsimple}
\usepackage{pgfplotstable}
\usepackage{array}
%\usepackage{colortbl}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{dsfont}
\usepackage{amsxtra}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage{comment}

\usepackage{multirow}
\usepackage{url}

\usepackage{graphicx,epsfig}
%\usepackage{dcolumn}
%\usepackage{bm}
%\usepackage{ulem}

\usepackage{xspace} 

\usepackage{color}
\usepackage{xcolor}

\usepackage{lineno}
\linenumbers
\usepackage[export]{adjustbox}


\renewcommand{\baselinestretch}{1.2}

%\setlength{\textwidth}{17.5cm} 
%\setlength{\textheight}{24.cm}
%\setlength{\topmargin}{-1.5cm}
%\setlength{\oddsidemargin}{-0.4cm}


\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\beaa}{\begin{eqnarray*}}
\newcommand{\eeaa}{\end{eqnarray*}}
\newcommand{\ba}{\begin{array}}	
\newcommand{\ea}{\end{array}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\ben}{\begin{enumerate}}
\newcommand{\een}{\end{enumerate}}

\newcommand{\bra}{\langle}
\newcommand{\ket}{\rangle}
\newcommand{\ra}{\rightarrow}
\newcommand{\lra}{\longrightarrow}
\newcommand{\overar}{\overrightarrow}
\newcommand{\wt}{\widetilde}
\newcommand{\td}{\tilde}


\newcommand{\lb}{\label}
\newcommand{\g}{\ensuremath{\gamma}\xspace}
\newcommand{\G}{\Gamma}
\newcommand{\e}{\epsilon}
\newcommand{\al}{\alpha}
\newcommand{\bt}{\beta}
\newcommand{\p}{\partial}
\newcommand{\dl}{\delta}
\newcommand{\Dl}{\Delta}
\newcommand{\ld}{\lambda}
\newcommand{\Ld}{\Lambda}
\newcommand{\vp}{\varphi}
\newcommand{\te}{\theta}
\newcommand{\Om}{\Omega}
\newcommand{\om}{\omega}
\newcommand{\sm}{\sigma}
\newcommand{\Sm}{\Sigma}

\newcommand{\A}{{\rm A}}
\newcommand{\B}{{\rm B}}
\newcommand{\U}{{\rm U}}
\newcommand{\F}{{\rm F}}
\newcommand{\SU}{{\rm SU}}
\newcommand{\Tr}{{\rm Tr}}
\newcommand{\Hom}{{\rm Hom}}

\newcommand{\FF}{{\mathsf F}}

\newcommand{\mcE}{{\mathcal{E}}}
\newcommand{\N}{{\mathcal{N}}}
\newcommand{\D}{{\mathcal{D}}}
\newcommand{\La}{{\mathcal{L}}}
\newcommand{\OO}{{\mathcal{O}}}
\newcommand{\M}{{\mathcal{M}}}


\newcommand{\mbE}{{\mathbb{E}}}
\newcommand{\Z}{{\mathbb{Z}}}
\newcommand{\R}{{\mathbb{R}}}
\newcommand{\C}{{\mathbb{C}}}
\newcommand{\NN}{{\mathbb{N}}}
\newcommand{\PP}{{\mathbb{C}}{\rm P}}

\newcommand{\HH}{{\mathcal{H}}}
\newcommand{\Hd}{{\mathcal{H}}^*}

\newcommand{\HI}{H~\textsc{i}\xspace}
\newcommand{\Htwo}{$\mathrm{H}_2$\xspace}
\newcommand{\hi}{$\mathrm{H\,\scriptstyle{I}}$\xspace}
\newcommand{\hii}{$\mathrm{H\,\scriptstyle{II}}$\xspace}
\newcommand{\hd}{$\mathrm{H}_2$\xspace}
\newcommand{\xco}{$X_\mathrm{CO}$\xspace}

\newcommand{\vx}{{\bf x}}

\newcommand{\Fermi}{\textit{Fermi}\xspace}
\newcommand{\LAT}{\textsl{LAT}\xspace}
\newcommand{\WMAP}{\textsl{WMAP}\xspace}
\newcommand{\Planck}{\textsl{Planck}\xspace}
\newcommand{\Suzaku}{\textsl{Suzaku}\xspace}

\newcommand{\SM}{Sample Model\xspace}

\newcommand{\sigmav}{\ensuremath{\langle \sigma v \rangle}\xspace}
\newcommand{\bbbar}{\ensuremath{b \bar b}\xspace}
\newcommand{\tautau}{\ensuremath{\tau^{+}\tau^{-}}\xspace}
\newcommand{\relic}{\ensuremath{2.2\times10^{-26}\cm^{3}\second^{-1}}\xspace}
\newcommand{\beff}{\ensuremath{b_{\rm eff}}\xspace}
\newcommand{\DM}{\ensuremath{\mathrm{DM}}}
\newcommand{\mDM}{\ensuremath{m_\DM}\xspace}


% local options
\newcommand{\onepic}{0.45}
\newcommand{\twocolumnwidth}{0.75}
%\newcommand{\twopic}{0.38}
\newcommand{\twopic}{0.3}
\newcommand{\twopicsp}{0.45}
\newcommand{\threepic}{0.25}
%\newcommand{\threepic}{0.18}
\newcommand{\fourpic}{0.28}
\newcommand{\twopicwca}{0.35}

\newcommand{\cmap}{_afmhot}


\newcommand{\red}{\textcolor{red}}
\newcommand{\blue}{\textcolor{blue}}
\definecolor{darkgreen}{rgb}{0.0, 0.7, 0.0}
\newcommand{\green}{\textcolor{darkgreen}}

\newcommand{\dima}[1]{\textcolor{blue}{(Dima: #1)}}


\begin{document} 



   \title{Machine learning methods for constructing \\ probabilistic \Fermi-LAT catalogs}



   \author{A. Bhat \thanks{\email{aakash.bhat@fau.de}}
          \inst{1}
          \and
          D. Malyshev \thanks{on leave of absence from NRC ``Kurchatov Institute'' - ITEP, B. Cheremushkinskaya st. 25, Moscow, Russia 117218, 
          \email{dmitry.malyshev@fau.de}}
          \inst{1}
          }

   \institute{
             Erlangen Centre for Astroparticle Physics, Erwin-Rommel-Str. 1, Erlangen, Germany
             }

   \institute{
             Erlangen Centre for Astroparticle Physics, Erwin-Rommel-Str. 1, Erlangen, Germany
             }


 
\abstract
% context heading (optional)
% {} leave it empty if necessary  
{
Classification of sources is one of the most important tasks in astronomy.
Sources detected in one wavelength band, for example using gamma rays, may have several possible associations in other wavebands or
there may be no plausible association candidates.
}
% aims heading (mandatory)
{
In this work, we aim to determine probabilistic classification of unassociated sources in the third and the fourth data release 2 \Fermi Large Area Telescope (LAT) point source catalogs (3FGL and 4FGL-DR2) into two classes (pulsars and active galactic nuclei (AGNs)) or three classes (pulsars, AGNs, and other sources).
}
% methods heading (mandatory)
{
We use several machine learning (ML) methods to determine a probabilistic classification of \Fermi-LAT sources.
We evaluate the dependence of results on meta-parameters of the ML methods, such as the maximal depth of the trees in tree-based classification methods and the number of neurons in neural networks.
}
% results heading (mandatory)
{
We determine a probabilistic classification of both associated and unassociated sources in 3FGL and 4FGL-DR2 catalogs.
We cross-check the accuracy by comparing the predicted classes of unassociated sources in 3FGL with their associations in 4FGL-DR2, for cases where such associations exist.
We find that in the 2-class case it is important to correct for the presence of other sources among the unassociated ones in order to realistically estimate the number of pulsars and AGNs.
We find that the 3-class classification, in spite of different types of sources in the OTHER class, has similar performance as the 2-class classification in terms of reliability diagrams and, at the same time, it does not require adjustment due to presence of the OTHER sources among the unassociated sources.
We show an example of the use of the probabilistic catalogs for population studies, which include associated and 
unassociated sources.
}
% conclusions heading (optional), leave it empty if necessary 
{}

\keywords{Methods: statistical --
                Catalogs --
                Gamma rays: general
                %Galaxy: halo --
                %Galaxy: structure -- 
                %ISM: jets and outflows
               }

\maketitle

\tableofcontents


\input{1intro_pcat}
\input{2methods}
\input{3prediction}
\input{4multiclass}
\input{5comparison}
\input{6conclusions}

%\newpage
\bibliography{ML_3FGL_papers}  

\begin{appendix}
\input{app1and2}
\input{app3_reliability}
\input{app4_thresholds}

\end{appendix}

\end{document}

